### 2013-12-20 paper/main.tex
applied Matlab compatibilies with Octave
Various changes which make the M-Files compatible
with both Matlab and Octave have been applied.
Octave is surprising compatible.  Only once case,
converting a z-domain transfor to state space,
hasn't been resolved.

- removed 'endfunction'
- removed 'endfor', replaced with 'end'
- Matlab does not support default function arguments,
  used 'narg' instead.
- Matlab accepts 'InputName' instead of 'inname' and
  'OutputName' instead of 'outname' for the control toolbox.

% {{{ fig:em_plot
\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.7]{../octave/em_plot1}
\end{center}
\caption{Output response of engine model with no control.
The control can range from zero to one.
Here the control is constant at 0.65 which resulted in a stable
rpm near 900.}
\label{fig:em_plot}
\end{figure}
% }}}

@@

% {{{ fig:rpmtime_plot
\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.7]{../octave/em_plot2}
\end{center}
\caption{Engine rpm response compared to time with a constant
0.65 input control.}
\label{fig:rpmtime_plot}
\end{figure}
% }}}

@@

% {{{ fig:em_plot4
\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.6]{../octave/em_plot4}
\end{center}
\caption{Response for a shifted and scaled step input with zero torque.}
\label{fig:em_plot4}
\end{figure}
% }}}

@@

% {{{ fig:dd_plot2
\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.6]{../octave/dd_plot2}
\end{center}
\caption{Output response of controller built using Direct Design
compared to no control.  For no control this is the same plot
as in Figure \ref{fig:em_plot4} which stabilizes after a second.
The Matlab source performing these calculations and producing this
plot is given in Appendix \ref{app:dd_matlab}.}
\label{fig:dd_plot2}
\end{figure}
% }}}

@@

% {{{ fig:cl_plot1
\begin{figure}[!htp]
\begin{center}
\includegraphics[scale=0.6]{../octave/cl_ff01}
\end{center}
\caption{Output response of Control Law regulator with $K = 0.01$
and rpm = $700$.
Rpm was allowed to stabilize at 200 rpm before applying a step
to 700 rpm.
Source code is provided in Appendix \ref{app:cl_matlab}.}
\label{fig:cl_plot1}
\end{figure}
% }}}

@@

\begin{figure}[htbp!]
\includegraphics[scale=0.7]{../octave/cd_plot1}
\caption{Response of full steady state input to delta output system
to an arbitrary input signal.
The upper plot is the input signal ($u$) and the lower plot is
the output response ($y$).
The Matlab source code is given in Listing \ref{lst:cd_plot1}.
}
\label{fig:cd_plot1}
\end{figure}

@@

\begin{figure}[htbp!]
\includegraphics[scale=0.7]{../octave/cd_plot2}
\caption{Response of simplified steady state input to delta output system
to an arbitrary input signal.
The upper plot is the input signal ($u$) and the lower plot is
the output response ($y$).
Response is identical to the full system in Figure \ref{fig:cd_plot1}
as expected.
The Matlab source code is given in Listing \ref{lst:cd_plot2}.
}
\label{fig:cd_plot2}
\end{figure}

@@

\lstinputlisting[caption={Matlab code to plot the full steady state
to delta system.},
	label=lst:cd_plot1
	]{../octave/cd_plot1.m}

\clearpage
\lstinputlisting[caption={Matlab code to plot the simplified steady state
to delta system.},
	label=lst:cd_plot2
	]{../octave/cd_plot2.m}

@@

% {{{ fig:dc_plot2
\begin{figure}[htbp!]
\includegraphics[scale=0.7]{../octave/dc_plot2}
\caption{Response of delta input to steady state output system
when given an arbitrary input signal.
The upper plot is the input signal ($u$) and the lower plot is
the output response ($y$).
The Matlab source code is given in Listing \ref{lst:dc_plot2}.
}
\label{fig:dc_plot2}
\end{figure}
% }}}

@@

\lstinputlisting[caption={Matlab code to plot the simplified steady state
to delta system.},
	label=lst:dc_plot2
	]{../octave/dc_plot2.m}

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.5]{../octave/em_plot3}
\end{center}
\caption{Stable rpm reached for a given constant control input.}
\label{fig:stable}
\end{figure}

\clearpage
\lstinputlisting[
	caption={Matlab source to find the stable rpm for a given
		control input.},
	label={lst:stable}
	]{../octave/em_plot3.m}
% }}}

@@

\lstinputlisting[
	caption={Matlab source to calculate the engine model system with
		zero torque.  This function is called by other scripts that
	use this model.}
	]{../octave/engine_model.m}

\lstinputlisting[
	caption={Matlab source to plot the response of engine model
		with no control. The $x$ axis is in ticks.}
	]{../octave/em_plot1.m}

% XXX
\clearpage
\lstinputlisting[
	caption={Matlab source to plot the response of engine model
	with no control.  The $x$ axis is in time.}
	]{../octave/em_plot2.m}

\clearpage
\lstinputlisting[
	caption={Matlab source to plot the response of engine model
		versus time for a typical 600 to 1000 rpm range.}
	]{../octave/em_plot4.m}
% }}}

@@

\lstinputlisting[
	caption={Matlab source of function to calculate a Sylvester Matrix.} 
	]{../octave/sylvester.m}

\lstinputlisting[
	caption={Matlab source of function to calculate zero time.} 
	]{../octave/zerotime.m}

\clearpage
\lstinputlisting[
	caption={Matlab source of modified lsim() function.} 
	]{../octave/lsim1.m}

@@

\lstinputlisting[
	caption={Matlab source of function is to build a controller using
		Direct Design.}
	]{../octave/direct_design.m}

\clearpage
\lstinputlisting[
	caption={Matlab source used to plot the controller built using
	Direct Design compared to no control.}
	]{../octave/dd_plot2.m}

@@

\lstinputlisting[
	caption={Matlab source used to plot the Control Law regulator.}
	]{../octave/cl_ff01.m}

@@

This written in \LaTeX and built using Pdflatex.
The block diagrams were written using TikZ\autocite{tikz}.
All calculations and plots were run using version 3.6.4 of
Octave\autocite{octave}, an open source Matlab clone.
When possible the examples were tested in Matlab/Simulink.
However much of the code is dependent upon the
Octave Control (CACSD) Tools\autocite{octave-control} which are
not entirely compatible with Matlab.
This document and all of its code are released under the
GNU General Public License and freely
available\autocite{github_jmahler_idle-control}.
\nocite{github_jmahler_control}

>>>>

% {{{ fig:em_plot
\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.7]{../matlab/em_plot1}
\end{center}
\caption{Output response of engine model with no control.
The control can range from zero to one.
Here the control is constant at 0.65 which resulted in a stable
rpm near 900.}
\label{fig:em_plot}
\end{figure}
% }}}

@@

% {{{ fig:rpmtime_plot
\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.7]{../matlab/em_plot2}
\end{center}
\caption{Engine rpm response compared to time with a constant
0.65 input control.}
\label{fig:rpmtime_plot}
\end{figure}
% }}}

@@

% {{{ fig:em_plot4
\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.6]{../matlab/em_plot4}
\end{center}
\caption{Response for a shifted and scaled step input with zero torque.}
\label{fig:em_plot4}
\end{figure}
% }}}

@@

% {{{ fig:dd_plot2
\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.6]{../matlab/dd_plot2}
\end{center}
\caption{Output response of controller built using Direct Design
compared to no control.  For no control this is the same plot
as in Figure \ref{fig:em_plot4} which stabilizes after a second.
The Matlab source performing these calculations and producing this
plot is given in Appendix \ref{app:dd_matlab}.}
\label{fig:dd_plot2}
\end{figure}
% }}}

@@

% {{{ fig:cl_plot1
\begin{figure}[!htp]
\begin{center}
\includegraphics[scale=0.6]{../matlab/cl_ff01}
\end{center}
\caption{Output response of Control Law regulator with $K = 0.01$
and rpm = $700$.
Rpm was allowed to stabilize at 200 rpm before applying a step
to 700 rpm.
Source code is provided in Appendix \ref{app:cl_matlab}.}
\label{fig:cl_plot1}
\end{figure}
% }}}

@@

\begin{figure}[htbp!]
\includegraphics[scale=0.7]{../matlab/cd_plot1}
\caption{Response of full steady state input to delta output system
to an arbitrary input signal.
The upper plot is the input signal ($u$) and the lower plot is
the output response ($y$).
The Matlab source code is given in Listing \ref{lst:cd_plot1}.
}
\label{fig:cd_plot1}
\end{figure}

@@

\begin{figure}[htbp!]
\includegraphics[scale=0.7]{../matlab/cd_plot2}
\caption{Response of simplified steady state input to delta output system
to an arbitrary input signal.
The upper plot is the input signal ($u$) and the lower plot is
the output response ($y$).
Response is identical to the full system in Figure \ref{fig:cd_plot1}
as expected.
The Matlab source code is given in Listing \ref{lst:cd_plot2}.
}
\label{fig:cd_plot2}
\end{figure}

@@

\lstinputlisting[caption={Matlab code to plot the full steady state
to delta system.},
	label=lst:cd_plot1
	]{../matlab/cd_plot1.m}

\clearpage
\lstinputlisting[caption={Matlab code to plot the simplified steady state
to delta system.},
	label=lst:cd_plot2
	]{../matlab/cd_plot2.m}

@@

% {{{ fig:dc_plot2
\begin{figure}[htbp!]
\includegraphics[scale=0.7]{../matlab/dc_plot2}
\caption{Response of delta input to steady state output system
when given an arbitrary input signal.
The upper plot is the input signal ($u$) and the lower plot is
the output response ($y$).
The Matlab source code is given in Listing \ref{lst:dc_plot2}.
}
\label{fig:dc_plot2}
\end{figure}
% }}}

@@

\lstinputlisting[caption={Matlab code to plot the simplified steady state
to delta system.},
	label=lst:dc_plot2
	]{../matlab/dc_plot2.m}

@@

\begin{figure}[htbp!]
\begin{center}
\includegraphics[scale=0.5]{../matlab/em_plot3}
\end{center}
\caption{Stable rpm reached for a given constant control input.}
\label{fig:stable}
\end{figure}

\clearpage
\lstinputlisting[
	caption={Matlab source to find the stable rpm for a given
		control input.},
	label={lst:stable}
	]{../matlab/em_plot3.m}
% }}}

@@

\lstinputlisting[
	caption={Matlab source to calculate the engine model system with
		zero torque.  This function is called by other scripts that
	use this model.}
	]{../matlab/engine_model.m}

\lstinputlisting[
	caption={Matlab source to plot the response of engine model
		with no control. The $x$ axis is in ticks.}
	]{../matlab/em_plot1.m}

% XXX
\clearpage
\lstinputlisting[
	caption={Matlab source to plot the response of engine model
	with no control.  The $x$ axis is in time.}
	]{../matlab/em_plot2.m}

\clearpage
\lstinputlisting[
	caption={Matlab source to plot the response of engine model
		versus time for a typical 600 to 1000 rpm range.}
	]{../matlab/em_plot4.m}
% }}}

@@

\lstinputlisting[
	caption={Matlab source of function to calculate a Sylvester Matrix.} 
	]{../matlab/sylvester.m}

\lstinputlisting[
	caption={Matlab source of function to calculate zero time.} 
	]{../matlab/zerotime.m}

\clearpage
\lstinputlisting[
	caption={Matlab source of modified lsim() function.} 
	]{../matlab/lsim1.m}

@@

\lstinputlisting[
	caption={Matlab source of function is to build a controller using
		Direct Design.}
	]{../matlab/direct_design.m}

\clearpage
\lstinputlisting[
	caption={Matlab source used to plot the controller built using
	Direct Design compared to no control.}
	]{../matlab/dd_plot2.m}

@@

\lstinputlisting[
	caption={Matlab source used to plot the Control Law regulator.}
	]{../matlab/cl_ff01.m}

@@

This written in \LaTeX and built using Pdflatex.
The block diagrams were written using TikZ\autocite{tikz}.
All calculations and plots were run using version 3.6.4 of
Octave\autocite{octave}, an open source Matlab clone.
Except for a few instances (\verb+cl_fonp02.m+, \verb+cl_fonp03.m+) the
M-Files are completely compatible between both Octave and Matlab.
The entire control system is built within the M-File and has
no dependence on Simulink.
Octave uses the Octave Control (CACSD) Tools\autocite{octave-control} 
which have equivalents in Matlab.
In a few cases an equivalent Simulink diagram was built and in
each of the cases the results agreed.
This document and all of its code are released under the
GNU General Public License and freely
available\autocite{github_jmahler_idle-control}.
\nocite{github_jmahler_control}
